A Formal Model of Checked C

### 2023-01-16 sandp23/limitations.tex
Updating conclusion

\section{Limitations}
\label{sec:limitations}
We cannot handling function pointer calls to tainted function.

>>>>

\section{Limitations and Future Work}
\label{sec:limitations}
Despite the effectiveness of~\systemname{}, it has the following limitations:

\noindent\textbf{Sandbox Dependency:} \systemname{} assumes the availability of a sandbox and consequently inherits all the limitations of the corresponding sandbox.~\eg Programs should be compilable with the sandbox compiler.
Also, as shown in~\sect{subsec:programoverhead}, the performance of the partitioned applications mainly depends on the sandbox.
However, our implementation is not dependent on one specific sandbox and can be easily extended to other sandboxes. As part of our future work, we will extend our implementation to other sandboxes.

\noindent\textbf{Annotation Effort:} Currently, all~\code{taint} annotations have to be done manually -- such that these annotations satisfy our type checker rules (\sect{sec:typechecking}).
This could be tedious based on the complexity of the sandboxed function, its parameter complexity, and its dependency on other functions.
We plan to develop an automated annotation tool such that, given the initial annotations (\lst{lst:humantaint}), our tool will automatically add all the required annotations (\lst{lst:humanadjust}) according to our type rules.
